### 2017-10-18 Draft2/Appendix.tex
Add proofs for big-P properties

\begin{theorem}
	$\biggo$ merges over multiplication and division. That is,
	\begin{align*}
	\biggo(f(n)) \cdot \biggo(g(n)) &= \biggo(f(n) \cdot g(n))\\
	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
	\end{align*}
\end{theorem}

>>>>

\begin{proof}
	We will consider the statement about addition first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:

	\textit{Let $f' \in \biggo(f(n))$ and $g' \in \biggo(g(n))$. Then $f' + g' \in \biggo(f(n) + g(n))$.}

	We can show this by using the limit definition of $\biggo$. For brevity, we will omit the parameter $n$ to each function. Since

	\begin{align*}
	\lim_{n \to \infty} \left( \frac{f' + g'}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{f'}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g'}{f + g} \right)\\
	&= \left( \lim_{n \to \infty} \frac{f'}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
	&\ \ \ \ \left( \lim_{n \to \infty} \frac{g'}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
	&= \lim_{n \to \infty} \left( \frac{f + g}{f + g} \right)\\
	&= 1
	\end{align*}

	it follows that $f' + g' \in \biggo(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
\end{proof}

\begin{theorem}
	$\biggo$ merges over multiplication and division. That is,
	\begin{align*}
	\biggo(f(n))\biggo(g(n)) &= \biggo(f(n)g(n))\\
	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about multiplication first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:

	\textit{Let $f' \in \biggo(f(n))$ and $g' \in \biggo(g(n))$. Then $f'g' \in \biggo(f(n)g(n))$.}

	We can show this easily by multiplying the limits corresponding to $f'$ and $g'$:

	\begin{align*}
	\lim_{n \to \infty} \frac{f'(n)}{f(n)} &= 1\\
	\lim_{n \to \infty} \frac{g'(n)}{g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac{f'(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{g'(n)}{g(n)} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{f'(n)g'(n)}{f(n)g(n)} &= 1
	\end{align*}

	it follows that $f'g' \in \biggo(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $g'$ before multiplying, resulting in

	\begin{align*}
	\lim_{n \to \infty} \frac{f'(n) / g'(n)}{f(n) / g(n)} = 1
	\end{align*}

	This implies $f' / g' \in \biggo(f(n) / g(n))$.
\end{proof}
